% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header
\name{DICKSON UKANG'A MUTSOTSO\\[14pt]}% the \\[12pt] adds a blank line after name

\address{ P.O. Box 625 (00605) \\   Uthiru, Kenya \\ +254.720.395.121}

\address{ukanga@ona.io}

\begin{resume}

\section{PROFESSIONAL EXPERIENCE}

\vspace{8pt}
\textbf{Ona} \hfill        \textbf{December 2013 - Present} \\
\emph{Co-Founder and Software Engineer}       \hfill   Nairobi

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Co-Founder of a software engineering and design firm that develops open source tools to help organizations make smarter use of data to address important global challenges.

 \end{itemize} \vspace{-4pt}

\vspace{8pt}
\textbf{Columbia Global Centers | Africa - Nairobi} \hfill        \textbf{April 2012 - November 2013} \\
\emph{Programmer, School of Engineering}       \hfill   Nairobi

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Develop, implement and support ict solutions for Millennium Villages Project in particular ChildCount+ and CommCare.
        \item Develop, implement and support data collection and data analysis software solutions for the Sustainable Engineering Lab, Earth Institute in particular formhub.org, pyxform and bamboo.io.
 \end{itemize} \vspace{-4pt}

\vspace{8pt}
\textbf{Earth Institute – Millennium VIllages Project} \hfill        \textbf{October 2011 - April 2012} \\
\emph{Programmer, Independent Contractor}       \hfill   Nairobi

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Develop, implement and support a web and web mobile phone based software solutions for Millennium Villages Project – ChildCount+.
        \item Develop MVP Health Indiccators Reports.
 \end{itemize} \vspace{-4pt}

\vspace{8pt}
\textbf{Tracom Services Limited} \hfill        \textbf{July 2011 - January 2012} \\
\emph{Enterprise Software Developer}       \hfill   Nairobi

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Solutions Innovation Research And Development: Bank Switches, Intranets Development, Web based banking solutions.
        \item IT Systems Management and Administartion: Linux, Weblogic, Developer Operations.
        \item Led Applications Quality Assurance and Testing team.
 \end{itemize} \vspace{-4pt}

\vspace{8pt}
\textbf{Millennium VIllages Project: Sauri Village} \hfill        \textbf{August 2009 - June 2011} \\
\emph{ICT Solutions Administrator}       \hfill   Kisumu

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Develop, implement and support a web and mobile based platforms for Millennium Villages Project – including  OpenMRS and ChildCount+ for community healh workers to monitor the health of women and children under 5 years old.
        \item Development of a national scale SMS based clinic based monitoring system in Uganda for FIND.
        \item Knowledge transfer and training.
        \item Technical Support.
        \item Project Management.
        \item Monitoring and Evaluation Support, development of health indicator reports.
 \end{itemize} \vspace{-4pt}
 
\vspace{8pt}
\textbf{NetExchange Solutions Limited} \hfill        \textbf{2008 - July 2009} \\
\emph{Web Developer}       \hfill   Nairobi

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Develop, implement and support a web based platforms for clients in the banking industry.
        \item Development of the Safaricom IPO online registration and Safaricom IPO Back Office web applications.
 \end{itemize} \vspace{-4pt}
 
\vspace{8pt}
\textbf{Munaalu Distributers} \hfill        \textbf{February 2003 - March 2004} \\
\emph{Shop Assistant}       \hfill   Kakamega

\begin{itemize} \itemsep -2pt % reduce space between items
        \item Customer Relations and stock taking
\end{itemize} \vspace{-4pt}


\section{EDUCATION}
\vspace{8pt}
\textbf{Kenyatta University}  \\
\emph{Bachelor of Science Computer Science} \hfill \textbf{2004 - 2008}
   \begin{itemize} \itemsep -2pt % reduce space between items
        \item Internship at Swift Technologies \hfill   April - August, 2007
        \item An active member  in Computer  Science Club Kenyatta University, I was Project Coordinator in 2007/2008.
        \item Participant on the 2007 IEEE Exhibition in the mobile applications category.
        \item Attended Python for Nokia Symbian OS bootcamp at University of Nairobi, conducted by Nathan Eagle - MIT
    \end{itemize} \vspace{-6pt}

\vspace{8pt}
\textbf{Nairobi School}  \\
\emph{High School} \hfill \textbf{1999 - 2002}
    \begin{itemize} \itemsep -2pt % reduce space between items
        \item Involved in the Juniour Achievement Program.
        \item I was a member of SCAD (Students Campaign Against Drugs).
    \end{itemize}


\section{REFEREES}
\vspace{8pt}
\textbf{Mr. Francis G. Kenyaga}  \\
Business Development  Director  \\
Tracom Services Limited  \\
P.O Box 25749 ­ 00603 \\
Nairobi, Kenya \\
Tel: +254 20 242 9692/3 \\
Cell: +254 722 816010 \\
Email: francis.gitau@tracom.co.ke

\textbf{Margaret Ndisha} \\
IT Officer In­charge,  \\
Ministry of Public Health Services (DLTLD) ­ Global Fund Project  \\
Nairobi, Kenya  \\
Cell: +254 726 537438  \\
E­mail: mndisha@nltp.co.ke,  mndisha@gmail.com

\textbf{Esther Wamoto}  \\
Human Resource Officer  \\
Columbia Global Centers | Africa  \\
Tel: +254 20 444 06 12/3/4  \\
P.O. Box  51412 GPO 00100  \\
Nairobi

\section{LANGUAGES}
\vspace{8pt}
English (Fluent), Kiswahili (Fluent)

\section{GEOGRAPHIC WORK EXPERIENCE}
\vspace{8pt}
Kenya, Uganda, India

\end{resume}
\end{document}
